The Value of Forecasting: The Effect of Building Load Forecast Errors on the Performance of an Optimal Energy Management System

### 2024-07-16 paper/paper.tex
final work for paper

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{The Value of Forecasting: The Effect of Building Load Forecast Errors on the Performance of an Optimal Energy Management System}

\author{\IEEEauthorblockN{Michael Wood}
\IEEEauthorblockA{Energy Department\\
Politecnico di Milano\\
Milan, Italy\\
Email: michael.wood@polimi.it}
\and
\IEEEauthorblockN{Emanuele Ogliari}
\IEEEauthorblockA{Energy Department\\
Politecnico di Milano\\
Milan, Italy\\
}
%\and
%\IEEEauthorblockN{Travis Simpkins}
%\IEEEauthorblockA{muGrid Analytics\\
%Littleton, CO, USA\\
%}
\and
\IEEEauthorblockN{Sonia Leva}
\IEEEauthorblockA{Energy Department\\
Politecnico di Milano\\
Milan, Italy\\
}
}

@@

\begin{abstract}
    Distributed renewable microgrids will be a crucial technology during the energy transition. Still, many vehicle-to-grid, demand response, and storage battery resources are not utilized fully to reduce consumer electric costs or support the larger grid as needed. This is due to poor integration between systems, but also because of a challenging forecasting problem that is required to be solved to achieve near-optimal unit commitment. Traditional forecasting methods and also modern machine learning algorithms are often trained and evaluated on mean squared error, which may not optimize for or predict the performance of a forecast in an optimal energy management system. This novel work constructs several different forecasts with different error distributions to study the impact on simulated optimal battery dispatch. The findings are that forecast error is most important during peak load periods and peak price periods, especially with consumer demand charges in place, and a zero-bias forecast is not necessarily advantageous. Recommendations are made to train and validate forecasting models to be effective with a downstream decision maker and not simply be optimized for a chosen error metric.
    \end{abstract}

@@

Energy optimization relies heavily on accurate forecasts of electric load, dynamic prices, and renewable energy generation. From large power systems to small building microgrids, peak load events or sudden drops in solar generation can be mitigated with control actions such as demand response or dispatchable generation such as energy storage. However, depending on the control action, the cost of inaction, and other variables such as market opening and closing times, forecasting is required to anticipate the changes in load or generation, for instance by having enough State of Charge (SOC) in energy storage. This forecast-response paradigm will be increasingly important as certain regions experience more extreme weather events, and renewable generation adds uncertainty to power systems and markets.

For these reasons, errors in forecasts can significantly impact the efficiency and reliability of large and small power systems. And since forecasts are always acted upon by some downstream decision maker, a discussion of the forecast errors must also consider the decision maker. Therefore this work examines recent literature forecasting error in power systems and then simulates several statistically diverse forecasts in an optimal Energy Management System (EMS) to evaluate the effect of forecast error on the system's performance.

@@

Electric load forecasting is likely the oldest forecast in power systems. Long-term forecasts on the order of years were required to plan new generation and transmission infrastructure. Medium-term forecasts on the order of months were soon required to manage seasonal variations in load, especially regarding fuel storage and generator maintenance periods. In more recent times, short-term forecasts on the order of hours to a few days aided transmission operators in managing congestion and informed market participants after the re-regulation of energy markets in the latter half of the 20th century. Most recently, nowcasting on the order of minutes has become important to manage building and campus generation and loads in real-time, which don't benefit from the spatial aggregation of loads, and thus have more load variability.

Techniques for load forecasting include traditional statistical methods such as SARIMA and modern machine learning approaches like neural networks and support vector machines. According to \cite{b1}, while statistical methods offer robustness, machine learning models provide higher accuracy due to their ability to capture nonlinear patterns in the data. However, load forecasting errors can arise from various exogenous sources, including sudden weather changes, economic activities, and random anomalies in consumer behavior. In \cite{b2} authors emphasize the importance of error decomposition, which involves breaking down the total forecast error into systematic and random components, to better understand and mitigate the sources of inaccuracies.

@@

Solar power forecasting involves predicting the amount of power generated by solar PV systems. The error of these forecasts is affected by factors such as cloud cover, different types and elevations of clouds, temperature, wind, and electrical or mechanical phenomena in the PV system such as cell degradation and soiling. Typically the input features to a solar prediction model include a numerical weather prediction forecast and terrestrial solar radiation estimated by a clear sky model, such as in \cite{b7}.

Researchers in \cite{b3} demonstrated that statistical methods like ARIMA can be adapted for solar forecasting but often fall short in capturing the high variability. Instead, machine learning techniques, including ensemble methods and hybrid physically informed neural networks have shown improved performance as in \cite{b4} and \cite{b7}. Solar forecasting errors are often characterized by their dependence on weather conditions more than autocorrelation, making integration with real-time weather data critical.

\begin{figure}
    \centering
    \includegraphics[width=1\linewidth]{flowchart.png}
    \caption{Simulation Flowchart. The ReOpt software is given as inputs an hourly load forecast, an hourly solar forecast, specification of the retail electric tariff, and technical constraints such as the size of the battery. The output is the hourly battery dispatch vector, which is optimal for the given inputs. The assumption is the battery dispatch vector is now directly in operation. Calculating the site load from the true load and solar vectors allows to calculate the final cost of electricity.}
    \label{fig:flowchart}
\end{figure}

% \begin{figure}
%     \centering
%     \includegraphics[width=0.95\linewidth]{step1.png}
%     \caption{Simulation Step 1. The ReOpt software is given as inputs an hourly load forecast, an hourly solar forecast, specification of the retail electric tariff, and technical constraints such as the size of the battery. The outputs are an hourly battery dispatch vector, which is optimal for the given inputs, and the associated costs that would be incurred if the load and solar vectors were true.}
%     \label{fig:step1}
% \end{figure}

@@

Error analysis involves assessing the forecast accuracy using metrics such as Mean Absolute Error (MAE), Mean Squared Error (MSE), and Mean Absolute Percentage Error (MAPE), which are most common in deterministic forecasts. In \cite{b5} authors suggest that incorporating probabilistic forecasts, which provide a range of possible outcomes instead of a single point prediction, can enhance the robustness of energy optimization strategies. Therefore probabilistic metrics are needed also, such as the Prediction Interval Coverage Probability (PICP) and Prediction Interval Normalized Average Width (PINAW). Error metrics are powerful tools for comparing forecast models and are often required for parameters fitting, and can even incorporate a benchmark prediction such as MASE, proposed in \cite{b9}.

Summary statistical metrics are helpful but often the shape of model residuals tells more of the story. A common problem is forecast bias, the tendency to have a non-zero mean for all forecasted values or just during certain intervals. This may especially occur for particular clusters of intervals with common physical phenomena, such as grid outages or extreme weather events. Extreme magnitude clusters can have a large impact on the EMS performance and be difficult to predict, especially if the events are quite rare \cite{b10}.

Mitigating forecasting errors involves both improving forecast models and developing strategies to manage uncertainty. Authors in \cite{b6} highlight the use of ensemble forecasting, where multiple models are used to generate a range of possible outcomes, thus providing a measure of the forecast uncertainty. In \cite{b6i} forecast uncertainty is mitigated with a strategy to minimize starting SOC of a hot sodium nickel battery. Additionally, reinforcement learning algorithms can continuously learn and adjust from new data can help reduce errors over time. Bayesian statistics and approaches that consider decision-making under risk may aid the final EMS or decision-maker when the uncertainty is measurable \cite{b11}

\begin{figure}
    \centering
    \includegraphics[width=.87\linewidth]{one-line.png}
    \caption{The simulated system is a medium-sized municipal building in Wisconsin, USA, with actual on-site solar (111 kWp). A hypothetical 100 kW 200 kWh storage battery is simulated. Load and solar forecasts are derived from true 1-minute interval data form the site. One case study includes the real retail electric tariff at this site.}
    \label{fig:one-line}
\end{figure}

% \begin{figure}
%     \centering
%     \includegraphics[width=0.95\linewidth]{step2.png}
%     \caption{Simulation Step 2. The output battery dispatch vector is used, along with the true load and solar vectors, to calculate the grid exchange vector. This is then used to calculate what the actual retail electric cost would be if the battery had been dispatched according to the output from ReOpt.}
%     \label{fig:step2}
% \end{figure}

This paper aims to construct several statistically different electric load forecasts and simulate the performance of an optimal EMS. The EMS controls a storage battery to minimize the retail cost of electricity to a medium-sized municipal building. By keeping the MAE constant among almost all the forecasts, the differing final retail costs illustrate how the shape of forecast errors impacts the downstream decision-maker in specific ways.

Our main contribution to the literature is the novel approach of manually adding disturbances to the perfect forecast to create and study specific error distributions. The methodology is robust due to the use of true measured 1-minute interval electric load, true measured 1-minute solar PV production, a thoroughly validated optimal EMS (ReOpt by the National Renewable Energy Lab) \cite{b12}, a true retail electric tariff, and two modified tariffs to study the effects of price structures on the results. Simulation code and data are published on GitHub for reproducibility.

@@

@@

\subsection{ReOpt Simulations}

The study approach is a series of computer simulations. Each simulation consists of two steps, graphically depicted in Figure \ref{fig:flowchart}. Each simulation is performed on one year of time series data, solving the unit commitment problem for a behind-the-meter electric load, co-located solar photovoltaic (PV), and a co-located storage battery. The only controllable asset is the storage battery, which can charge or discharge in any time step within its technical limits of maximum power and SOC. When the perfect load forecast (true measured load) and perfect solar forecast (true measured solar) are simulated, the result is the theoretical optimal battery dispatch for that year of load and solar measurements. The following are some useful definitions:

\begin{itemize}
    \item Load consumption: $ L(i) \in \mathbb{R}_0^+ [kW]$
    \item Solar production: $ S(i) \in \mathbb{R}_0^+ [kW]$ 
    \item Battery net, charge, and discharge: $ B(i) \in \mathbb{R}  = B_{d}^+ - B_{c}^+ [kW]$
    \item Net load: $ L_{net} = L - S$
    \item Site load: $ L_{site} = L - S - B$
    \item True measured value: $ y_t(i) \in \mathbb{R}_0^+ $
    \item Forecasted value: $ y_f(i) \in \mathbb{R}_0^+ $
    \item Error: $ \epsilon \in \mathbb{R} = y_f - y_t $
    \item Time series interval: $ \Delta t \in \mathbb{R}^+ [h] $
\end{itemize}

If instead an imperfect load and solar forecast are provided, the result is the optimal battery dispatch given those inputs. In other words, the simulation finds a global minimum of retail electric cost believing the forecasted load and solar to be true. The simulation chooses the optimal battery dispatch given the forecasts and other inputs provided. Assuming that the battery dispatch is not modified by the EMS in the presence of true measurements, the imperfect forecasts result in a retail electric cost which is necessarily greater than or equal to the theoretical optimal given perfect forecasting.

ReOpt is a techno-economic distributed energy resource (DER) optimization tool, which is both free and open source, and is well validated in the literature \cite{b13}. It performs optimal operation and sizing of DERs, although it is not intended as a real-time optimal EMS. However, to optimally size DERs it must solve the unit commitment problem for one to several dispatchable DERs, which is the central task of an EMS. It does so by constructing and solving a mixed-integer linear program (MILP) which minimizes the life cycle cost of new and existing DERs from the perspective of the behind-the-meter DER owner. Binary decision variables are required, for instance, to prevent the battery from charging and discharging in the same time step. Depending somewhat on the particular solver used, optimality of the solution is guaranteed for moderate complexity problem formulations due to a convex cost function and continuously differentiable, linear constraints \cite{b14}. The tool is written using the JuMP library in the Julia programming language, but in this work the tool is accessed via web API and Python script.

@@

\begin{table}
    \centering
    \caption{Forecasts and Two Benchmarks}
    \label{tab:forecasts}
    \setlength{\tabcolsep}{3pt}
    %\begin{tabular}{@{}p{0.4cm} @{}p{2cm} l l l l l@{}}
    %\begin{tabular}{@{}p{3cm} @{}p{5cm}}
    \begin{tabular}{l l l}
        \hline
        Error Description       & Forecast                    & nMAE  \\
        \hline
        \hline
        Perfect                 & (1) \(y_{perfect} = y_t\)           & 0.0    \\
        \hline
        Constant                & (2a) \(y_f = y_t + k\)      & 0.1   \\
                                & (2b) \(y_f = y_t - k\)      & 0.1   \\
        \hline
        Linear                  & (3a) \(y_f = y_t + ky_t\)   & 0.1   \\
                                & (3b) \(y_f = y_t - ky_t\)   & 0.1   \\
        \hline
        Quadratic               & (4a) \(y_f = y_t + ky_t^2\) & 0.1   \\
                                & (4b) \(y_f = y_t - ky_t^2\) & 0.1   \\
        \hline
        Energy (Prices)         & (5a) \(y_f = y_t + kp_e\)   & 0.1   \\
                                & (5b) \(y_f = y_t - kp_e\)   & 0.1   \\
        \hline
        Demand (Prices)         & (6a) \(y_f = y_t + kp_d\)   & 0.1   \\
                                & (6b)\(y_f = y_t - kp_d\)    & 0.1   \\
        \hline
        Random (Gaussian)       & (7) \(y_f = y_t + X\)       & 0.1   \\
        \\
        \hline
        Persistence             & (8) \(y_{persist} = y_t(i-168)\)    & 0.033 \\
        \hline
        \hline
        Solar Only (no battery) & (9) No forecast             & n/a   \\
        \hline
    \end{tabular}
\end{table}

@@

\begin{enumerate}
\item One hypothesis is that errors during peak load periods is especially harmful to the EMS performance, especially when the rate tariff contains a price on peak demand, also called a demand charge.

\item A second hypothesis is that forecast errors during high energy prices is detrimental to EMS performance, especially in the absence of a demand charge.
\end{enumerate}

@@

A linear scaling factor $k$ is fit and applied separately to each forecast such that the normalized mean absolute error (nMAE) of each forecast is exactly 0.10. The value of 0.10 was determined experimentally to show a good spread of results: with an nMAE too low all the forecasts would be nearly perfect and indistinguishable, and vice versa.  The exceptions are that a perfect forecast will have an nMAE of zero, and a seasonal persistence forecast is possibly more interesting without other disturbances since it is already a good benchmark forecast \cite{b9}. By forcing all the manipulated forecasts to have the same nMAE, any differences in the EMS performance can be attributed to the shape of the error distribution and not just the magnitude.

@@

@@

\begin{align}
    C_t,m           & = \sum_{k=1}^K [p_{d,k,m}  max(L^+_{site,k,m})  \notag \\
                & + p_{e,k,m} \sum (L^+_{site,k,m}\Delta t)  \notag \\
                & + p_{s,k,m} \sum (L^-_{site,k,m}\Delta t) ] \label{eq:cost} \\
                 \text{subject to:}&  \notag \\
                L_{site,k,m}^+(i) & \ge 0 \text{ and } L_{site,k,m}^-(i) \le 0\ \forall\ i \notag \\
%\end{align}
%\begin{align*}
                \text{where:}& \notag \\
                k & \text{: TOU period} \notag \\
                K & \text{: total TOU periods} \notag \\
                m & \text{: month} \notag \\
    C_t,m         & \in \mathbb{R}^+ [\$] \text{: total monthly retail electric cost} \notag \\
    p_{x,k,m}     & \in \mathbb{R}^+ [\$/kW] \text{ or } [\$/kWh] \text{: price for TOU } k \notag 
\end{align}

\begin{table}
    \centering
    \caption{Retail Electric Tariff}
    \label{tab:tariff}
    \setlength{\tabcolsep}{3pt}
    %\begin{tabular}{@{}p{0.4cm} @{}p{2cm} l l l l l@{}}
    %\begin{tabular}{@{}p{3cm} @{}p{5cm}}
    \begin{tabular}{l l l l l}
        \hline
        Period & Hours & Buy Prices & Buy Prices & Sell Price  \\
         &  & (Jun 1 - Sep 30) & (Oct 1 - May 31) & (all months) \\
        \hline
        \hline
        Off peak & 0:00-9:00,  & 0.056 \$/kW  & 0.056 \$/kW & 0.050 \$/kWh \\
                  & 21:00-0:00 &              &        &       \\
        \hline
        Peak     & 9:00-21:00   & 0.075 \$/kWh, & 0.070 \$/kWh, & 0.050 \$/kWh \\
                 &              & 13 \$/kW & 11 \$/kW & \\
        \hline
    \end{tabular}
\end{table}

\begin{table}
    \centering
    \caption{Case Studies}
    \label{tab:case-studies}
    \setlength{\tabcolsep}{3pt}
    %\begin{tabular}{@{}p{0.4cm} @{}p{2cm} l l l l l@{}}
    %\begin{tabular}{@{}p{3cm} @{}p{5cm}}
    \begin{tabular}{l l l}
        \hline
        & Tariff & Modifications \\
        \hline
        \hline
        1 & Retail Electric Tariff (Table \ref{tab:tariff}) & \\
        2 & Retail Electric Tariff (Table \ref{tab:tariff}) & All \$/kW prices = 0  \\
        3 & Retail Electric Tariff (Table \ref{tab:tariff}) & Sell price = CA NEM3.0 \\
        \hline
    \end{tabular}
\end{table}

@@

\begin{align}
    P(C_x) [\frac{kW}{kW}]= & (C_x - C_{x,perfect}) \over (C_{x,solar-only} - C_{x,perfect}) \label{eq:performance} \\
    \text{where:}& \notag \\
    x  \in & \{e:\text{energy},d:\text{demand},r:\text{revenue},t:\text{total} \}  \notag \\
    C_x =& \text{ cost of forecast to be evaluated [\$]}  \notag \\
    C_{x,perfect} =& \text{ cost of perfect forecast [\$]}  \notag \\
    C_{x,solar-only} =& \text{ cost of solar-only benchmark [\$]}  \notag 
\end{align}

These two book-end benchmarks suggest a normalized performance metric where a sample cost value $C$ lies in the range between the perfect forecast (1) and solar-only benchmark (9). This "performance" $P$ takes a value of 0 when the forecast cost is equal to the solar-only benchmark and a value of 1 when the forecast cost equals the theoretical optimal.

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{The Value of Forecasting: The Effect of Building Load Forecast Errors on the Performance of an Optimal Energy Management System \\
\thanks{This study was carried out in MESSI – Management Energy Systems for Smart Islands project, within the PRIN PROGETTI DI RICERCA DI RILEVANTE INTERESSE NAZIONALE – Bando 2022 and received funding from the European Union Next-GenerationEU (PIANO NAZIONALE DI RIPRESAE RESILIENZA - PNRR MISSIONE 4 COMPONENTE 2, INVESTIMENTO 1.1 –D.D. n. 104 del 02/02/2022, 2022HMYX2C). This manuscript reflects only the authors’ views and opinions, neither the European Union nor the European Commission can be considered responsible for them.}}

\author{\IEEEauthorblockN{Michael Wood}
\IEEEauthorblockA{Department of Energy\\
Politecnico di Milano\\
Milan, Italy\\
Email: michael.wood@polimi.it}
\and
\IEEEauthorblockN{Emanuele Ogliari}
\IEEEauthorblockA{Department of Energy\\
Politecnico di Milano\\
Milan, Italy\\
}
\and
\IEEEauthorblockN{Sonia Leva}
\IEEEauthorblockA{Department of Energy\\
Politecnico di Milano\\
Milan, Italy\\
}
}

@@

\begin{abstract}
    Distributed renewable resources and microgrids will be a crucial technology during the energy transition. Fully utilizing these to reduce consumer electric costs will often necessitate forecasting electric load, required to solve the unit commitment problem. Traditional forecasting methods and also modern machine learning algorithms are often trained and evaluated on mean squared error, which may not be the best choice for designing forecasts that work effectively with a downstream decision maker: an optimal energy management system. This novel work constructs several different forecasts with different error distributions to study the error impact on simulated optimal battery dispatch in a building microgrid. The findings are that forecast error is most important during peak load periods and peak price periods, especially with consumer demand charges in place, and a zero-bias or random Gaussian error distribution is necessarily advantageous. 
    \end{abstract}

@@

Energy optimization relies heavily on accurate forecasts of electric load, dynamic prices, and renewable energy generation. From large power systems to small building microgrids, peak load events or sudden drops in solar generation can be mitigated with control actions such as demand response or dispatchable generation such as energy storage. However, depending on the control action, the cost of inaction, and other variables such as market opening and closing times, forecasting is required to anticipate the changes in load or generation, for instance by having enough State of Charge (SOC) in energy storage. %This forecast-response paradigm will be increasingly important as certain regions experience more extreme weather events, and renewable generation adds uncertainty to power systems and markets.

In a forecast-and-optimizer Energy Management System (EMS) approach, errors in forecasts can significantly impact the performance of downstream decision-makers. Therefore this work simulates several statistically diverse forecasts in an optimal EMS to evaluate the effect of forecast error on the system's performance.

@@

Electric load forecasting is likely the oldest forecast in power systems. Recently short-term forecasts, on the order of hours to a few days, have been very important in supporting stable and efficient real-time market and operational decisions such as managing transmission congestion and informing market participants of their day-ahead bidding strategies.

Techniques for load forecasting include traditional statistical methods such as SARIMA, but modern machine learning approaches like recurrent neural networks may improve typical error metrics as in \cite{wood2023day} and \cite{matrone2024electric}. Load forecasting errors can be inherent to the model or arise from various exogenous sources, including sudden weather changes, economic activities, and random anomalies in consumer behavior. In \cite{hong2016probabilistic} authors emphasize the importance of error decomposition, which involves breaking down the total forecast error into systematic and random components, to better understand and mitigate the sources of inaccuracies.

@@

Solar PV can be said to reduce the net load in many power systems because it is almost always dispatched immediately, having a near-zero marginal cost. Therefore a discussion of load forecasting errors should also consider solar PV forecast errors, which are affected by factors such as cloud cover, different types and elevations of clouds, temperature, wind, and electrical or mechanical phenomena in the PV system such as cell degradation and soiling \cite{leva2017analysis}.

Statistical methods like ARIMA can be adapted for solar forecasting but often fall short in capturing the high variability. Instead, machine learning techniques, including ensemble methods and hybrid physically informed neural networks have shown improved performance as in \cite{yang2018history} and \cite{matera2024time}.

\begin{figure}
    \centering
    \includegraphics[width=1\linewidth]{images/flowchart.png}
    \caption{Simulation Flowchart}
    \label{fig:flowchart}
\end{figure}

@@

Error analysis involves assessing the forecast accuracy using metrics. Common deterministic forecasts are Mean Absolute Error (MAE), Mean Squared Error (MSE),  Mean Absolute Percentage Error (MAPE), and Mean Absolute Scaled Error (MASE), the last of which scales to a simple persistence benchmark. Rather for stochastic methods, metrics are required such as the Prediction Interval Coverage Probability (PICP) and Prediction Interval Normalized Average Width (PINAW).  A common problem is forecast bias, the tendency to have a non-zero mean for all forecasted values or just during certain intervals. Large errors are also caused by out-of-sample physical phenomena, such as grid outages or extreme weather events. Extreme magnitude clusters can have a large impact on the EMS performance and be difficult to predict, especially if the events are quite rare \cite{cirillo2020tail}.

Mitigating forecasting errors involves both improving forecast models and developing strategies to manage uncertainty. Analysis in \cite{makridakis2022predicting} of the M5 competition results show that the highest performance methods often use ensemble approaches, where multiple models are used to generate a range of possible outcomes, thus providing a measure of the forecast uncertainty. In \cite{grillo2012optimal} forecast uncertainty is mitigated with a strategy to minimize the starting SOC of a hot sodium nickel battery. Bayesian deep learning \cite{sun2019using} and approaches that consider decision-making under risk may aid the final EMS or decision-maker when the uncertainty is measurable.

\begin{figure}
    \centering
    \includegraphics[width=.78\linewidth]{images/one-line.png}
    \caption{Site One-Line Diagram }
    \label{fig:one-line}
\end{figure}

This study's novel contribution to the literature is the approach of manually adding disturbances to the perfect forecast to create and study specific error distributions. The methodology is robust due to the use of true measured 1-minute interval electric load, true measured 1-minute solar PV production, a thoroughly validated optimal EMS (ReOpt by the National Renewable Energy Lab) \cite{simpkins2014reopt}, a true retail electric tariff, and two modified tariffs to study the effects of price structures on the results. Simulation code and data are published on GitHub for reproducibility.

@@

\begin{figure}
    \centering
    \includegraphics[width=1\linewidth]{images/weekly.png}
    \caption{Load Time Series}
    \label{fig:data-weekly}
\end{figure}
% The municipal building load overlaid weekly shows the daily seasonality, weekly seasonality, and much larger peaks which we confirm elsewhere to be during the summer months, and likely due to increased occupancy and air conditioning. The data is from one year of 1-minute interval average power measurements and is then mean downsampled to hourly for ReOpt.

@@

The study approach is a series of computer simulations that consist of two steps, graphically depicted in Fig.~\ref{fig:flowchart}. Each forecast-and-optimize simulation is performed on one year of time series data, solving the unit commitment problem for a behind-the-meter electric load, a co-located solar photovoltaic (PV) array, and a co-located storage battery. The only controllable asset is the storage battery, which can charge or discharge at any time step within its technical limits of maximum power and SOC. The following are some useful definitions:

\begin{itemize}
    \item Load consumption: $ L(i) \in \mathbb{R}_0^+ [kW]$
    \item Solar production: $ S(i) \in \mathbb{R}_0^+ [kW]$ 
    \item Battery charge, discharge: $ B_{c}(i), B_{d}(i) \in \mathbb{R}_0^+ [kW]$
    \item Battery net: $ B(i) \in \mathbb{R}  = B_{d} - B_{c}$
    \item Net load: $ L_{net} = L - S$
    \item Site load: $ L_{site} = L - S - B$
    \item True measured value: $ y_t(i) \in \mathbb{R}_0^+ $
    \item Forecasted value: $ y_f(i) \in \mathbb{R}_0^+ $
    \item Error: $ \epsilon \in \mathbb{R} = y_f - y_t $
    \item Time series interval: $ \Delta t \in \mathbb{R}^+ [h] $
\end{itemize}

\subsection{Optimizer}

The unit commitment problem is solved by a centralized optimizer which is capable of modeling the the controllable assets, in this case only the battery. There are two different and important cases to consider:

\begin{enumerate}
    \item \textbf{Perfect Forecasting.} When the perfect load forecast (true measured load) and perfect solar forecast (true measured solar) are simulated, the result is the theoretical optimal battery dispatch for that year of load and solar measurements.
    \item \textbf{Imperfect Forecasting.} If instead an imperfect load and solar forecast are provided, the result is the optimal battery dispatch as if those forecasts were the true values. In other words, the simulation finds a global minimum of retail electric cost believing the forecasted load and solar to be true. Assuming that the battery dispatch is not modified by the EMS in the presence of information about the true measurements, the imperfect forecasts result in a retail electric cost that is necessarily greater than or equal to the theoretical optimal given perfect forecasting.
\end{enumerate}

\subsubsection{ReOpt}

The optimizer in this study is ReOpt, a techno-economic distributed energy resource (DER) planning tool, which is well-validated in the literature \cite{mishra2022computational}. It performs optimal operation and sizing of DERs, although it is not intended as a real-time optimal EMS. However, to optimally size DERs it must solve the unit commitment problem for one to several dispatchable DERs, which is the central task of an EMS. It does so by constructing and solving a mixed-integer linear program (MILP) which minimizes the life cycle cost of new and existing DERs from the perspective of the behind-the-meter DER owner. Binary decision variables are required, for instance, to prevent the battery from charging and discharging at the same time step.

Depending somewhat on the particular solver used, optimality of the solution is guaranteed for moderate complexity problem formulations due to a convex cost function and continuously differentiable, linear constraints \cite{ogunmodede2021optimizing}. Some disadvantages of ReOpt are the hourly interval which may contribute to errors relative to a real system (\cite{omoyele2024impact}), that forecasts cannot be updating in a rolling horizon manner, and some real-world losses are not considered such as battery heating and cooling.

ReOpt is both free and open source and is written using the JuMP library in the Julia programming language. It can be accessed accessed via an interactive web application, or a web API and Python script as in the case of this study.

\begin{figure}
    \centering
    \includegraphics[width=1\linewidth]{images/hist.png}
    \caption{Error Distributions of Several Forecasts}
    \label{fig:hist}
\end{figure}

@@

@@

\begin{enumerate}
\item One hypothesis is that errors during peak load periods are especially harmful to the EMS performance, especially when the rate tariff contains a price on peak demand, also called a demand charge.

\item A second hypothesis is that forecast errors during high energy prices are detrimental to EMS performance, especially in the absence of a demand charge.
\end{enumerate}

@@

A linear scaling factor $k$ is fit and applied separately to each forecast such that the normalized mean absolute error (nMAE) of each forecast is exactly 0.10. The value of 0.10 was determined experimentally to show a good spread of results: with an nMAE too low all the forecasts would be nearly perfect and indistinguishable, and vice versa.  The exceptions are that a perfect forecast will have an nMAE of zero, and a seasonal persistence forecast is possibly more interesting without other disturbances since it is already a good benchmark forecast \cite{hyndman2006another}. By forcing all the manipulated forecasts to have the same nMAE, any differences in the EMS performance can be attributed to the shape of the error distribution and not just the magnitude.

@@

\begin{figure}
    \centering
    \includegraphics[width=1\linewidth]{images/perf_lines.png}
    \caption{Case Study 1 Performance}
    \label{fig:cs1-performance}
\end{figure}

@@

\begin{align}
    C_t,m           & = \sum_{k=1}^K [p_{d,k,m}  max(L^+_{site,k,m}) ...  \notag \\
                & +  \sum_{k=1}^K (p_{e,k,m} L^+_{site,k,m}\Delta t) ... \notag \\
                & +  \sum_{k=1}^K (p_{r,k,m} L^-_{site,k,m}\Delta t) ] \label{eq:cost} \\
                \text{where:}& \notag \\
                L_{site,k,m}^+(i) & \ge 0 \text{ and } L_{site,k,m}^-(i) \le 0\ \forall\ i \notag \\
                k & \text{: TOU period} \notag \\
                K & \text{: total TOU periods} \notag \\
                m & \text{: month} \notag \\
    C_t,m         & \in \mathbb{R}^+ [\$] \text{: total monthly retail electric cost} \notag \\
    p_{x,k,m}     & \in \mathbb{R}^+ [\$/kW] \text{ or } [\$/kWh] \text{: price for TOU } k \notag \\
    x \in & \{e:\text{energy},d:\text{demand},r:\text{revenue},t:\text{total} \}  \notag 
\end{align}

\begin{figure}
    \centering
    \includegraphics[width=1\linewidth]{images/monthly_peaks_lines.png}
    \caption{Case Study 1 Monthly Peaks}
    \label{fig:cs1-peaks}
\end{figure}

@@

\begin{align}
    P(C_x) [\%]= & \frac{C_x - C_{x,perfect}}{C_{x,solar-only} - C_{x,perfect}} \times 100\% \label{eq:performance} \\
    \text{where:}& \notag \\
    C_x =& \text{ cost of forecast to be evaluated [\$]}  \notag \\
    C_{x,perfect} =& \text{ cost of perfect forecast [\$]}  \notag \\
    C_{x,solar-only} =& \text{ cost of solar-only benchmark [\$]}  \notag \\
    x \in & \{e:\text{energy},d:\text{demand},r:\text{revenue},t:\text{total} \}  \notag 
\end{align}

These two book-end benchmarks suggest a normalized performance metric where a sample cost value $C$ lies in the range between the perfect forecast (1) and solar-only benchmark (9). This "performance" $P$ takes a value of 0\% when the forecast cost is equal to the solar-only benchmark and a value of 100\% when the forecast cost equals the theoretical optimal.

\begin{table}[t]
    \centering
    \caption{Forecasts and Solar-Only Benchmark}
    \label{tab:forecasts}
    \setlength{\tabcolsep}{9pt}
    \begin{tabular}{l l l l}
        %\hline
        Forecast               & Note                             & Definition & nMAE \\
        \hline
        \hline
        1 Perfect & Benchmark &  \(y_{perfect} = y_t\)        & 0.0               \\
        \hline
        2a Constant+ &             & \(y_f = y_t + k\)           & 0.1               \\
        2b Constant-  &            &  \(y_f = y_t - k\)           & 0.1               \\
        \hline
        3a Linear+     &           &  \(y_f = y_t + ky_t\)        & 0.1               \\
        3b Linear-      &          &  \(y_f = y_t - ky_t\)        & 0.1               \\
        \hline
        4a Quad+         &         &  \(y_f = y_t + ky_t^2\)      & 0.1               \\
        4b Quad-          &        &  \(y_f = y_t - ky_t^2\)      & 0.1               \\
        \hline
        5a Energy+ &Prices       &  \(y_f = y_t + kp_e\)        & 0.1               \\
        5b Energy- &Prices       &  \(y_f = y_t - kp_e\)        & 0.1               \\
        \hline
        6a Demand+ &Prices       &  \(y_f = y_t + kp_d\)        & 0.1               \\
        6b Demand- &Prices       &  \(y_f = y_t - kp_d\)        & 0.1               \\
        \hline
        7 Random &Gaussian      &  \(y_f = y_t + X\)            & 0.1               \\
        \hline
        8 Persist & 7 day               &  \(y_{persist} = y_t(i-168)\) & 0.033             \\
        \hline
        \hline
        9 Solar Only & Benchmark &  No forecast                  & n/a               \\
        \hline
    \end{tabular}
\end{table}

\begin{table}[t]
    \centering
    \caption{Retail Electric Tariff}
    \label{tab:tariff}
    \setlength{\tabcolsep}{3pt}
    \begin{tabular}{l l l l l}
        %\hline
        Period & Hours & Buy Prices & Buy Prices & Sell Price  \\
         &  & (Jun 1 - Sep 30) & (Oct 1 - May 31) & (all months) \\
        \hline
        \hline
        Off-peak & 0:00-9:00,  & 0.056 \$/kW  & 0.056 \$/kW & 0.050 \$/kWh \\
                  & 21:00-0:00 &              &        &       \\
        \hline
        Peak     & 9:00-21:00   & 0.075 \$/kWh, & 0.070 \$/kWh, & 0.050 \$/kWh \\
                 &              & 13 \$/kW & 11 \$/kW & \\
        \hline
    \end{tabular}
\end{table}

\begin{table}[t]
    \centering
    \caption{Case Studies}
    \label{tab:case-studies}
    \setlength{\tabcolsep}{6pt}
    \begin{tabular}{l l l}
        %\hline
        & Tariff & Modifications \\
        \hline
        \hline
        CS1 & Retail Electric Tariff (Table \ref{tab:tariff}) & \\
        CS2 & Retail Electric Tariff (Table \ref{tab:tariff}) & All \$/kW prices = 0  \\
        CS3 & Retail Electric Tariff (Table \ref{tab:tariff}) & Sell price = CA NEM3.0 \\
        \hline
    \end{tabular}
\end{table}
